### 2016-11-03 paper/evaluation.tex
updated setup sec

To run our experiments, we used a \emph{Core i7-4790} (3.60 GHz) Intel
processor machine with 8 virtual CPUs (4 cores with 2 native threads
each) and 16GB of memory, running \emph{Ubuntu 14.04 LTS Trusty Tahr}
(64-bit version). Our evaluation scripts depends on \Fix{specify:
unix-based tools} to measure CPU usage and \emph{Python 3.4} (or
later). For replication, we provide all the source artifacts publicly
available at \Fix{create gh-pages}, including supporting scripts (\eg,
the script that test subjects and generates the raw data), the full
list of projects, and a \emph{Vagrantfile} to emulate our hardware and
software setup and dependency settings .

>>>>

To run our experiments, we used a \emph{Core i7-4790} (3.60 GHz) Intel
processor machine with 8 virtual CPUs (4 cores with 2 native threads
each) and 16GB of memory, running \emph{Ubuntu 14.04 LTS Trusty Tahr}
(64-bit version). Software settings include the Linux \emph{sysstat}
package to measure performance, \emph{git} to fetch subjects,
\emph{Java 8} to build and test subjects, and \emph{Python 3.4} to run
our evaluation scripts. For replication, we provide all the source
artifacts publicly available at \Fix{create gh-pages}, including
supporting scripts (\eg, the script that test subjects and generates
the raw data), the full list of projects, and a \emph{Vagrantfile} to
emulate our hardware and all software dependencies properly configured.
